### 2019-05-09 tii/tex/impl.tex
Modify some fig.

\subsubsection{Context-Aware-Priority Constraint}
% Unlike the traditional cache replacement schemes such as MIN \cite{min}, the cached shuffle data will only be used once, but the legacy cache managements are designed to improve the hit rate.
{\color{blue}
SCache leverages application context to select victim storage units when the reserved memory is full.
At first, SCache flushes blocks of the incomplete units to disk cluster-widely.
If all the units are completed, SCache selects victims based on two factors: 
(a) For the tasks in the different stages, SCache sets the higher priority to storage units with a earlier submission time. 
(b) For the tasks in the same stage, SCache sets the higher priority to storage units with a smaller task ID.
}
% If all the units are completed, SCache selects victims based on two factors --- \textit{inter-shuffle} and \textit{intra-shuffle}.
% \begin{itemize}[noitemsep]
% 	\item Inter-shuffle: SCache master follows the scheduling scheme of Spark to determine the inter-shuffle priority. 
% 	% For example, Spark FIFO scheduler schedules the tasks of different stages according to the submission order. 
% 	SCache sets the priorities of tasks according to the submission time of each shuffle.
% 	% For a FAIR scheduler, Spark balances the resource among task sets, which leads to a higher priority for those having more tasks unfinished. 
% 	% So SCache sets priorities from high to low in a descending order of remaining storage units of a shuffle. 
% 	% For a FIFO scheduler, Spark schedules the task set that is submitted first. 
% 	% So SCache sets the priorities according to the submit time of each shuffle unit.
% 	\item Intra-shuffle: The intra-shuffle priorities are determined according to the task scheduling inside a stage.
% 	For example Spark schedules tasks with smaller ID at first. 
% 	Based on this, SCache can assign the lower priority to storage units with a larger task ID.
% \end{itemize}

>>>>

\subsubsection{Context-Aware-Priority Constraint}
% Unlike the traditional cache replacement schemes such as MIN \cite{min}, the cached shuffle data will only be used once, but the legacy cache managements are designed to improve the hit rate.
{\color{blue}
SCache leverages application context to select victim storage units when the reserved memory is full.
At first, SCache flushes blocks of the incomplete units to disk cluster-widely.
If all the units are completed, SCache selects victims based on two factors: 
(a) For the tasks in the different stages, SCache sets the higher priority to storage units with a earlier submission time;
(b) For the tasks in the same stage, SCache sets the higher priority to storage units with a smaller task ID.
}
% If all the units are completed, SCache selects victims based on two factors --- \textit{inter-shuffle} and \textit{intra-shuffle}.
% \begin{itemize}[noitemsep]
% 	\item Inter-shuffle: SCache master follows the scheduling scheme of Spark to determine the inter-shuffle priority. 
% 	% For example, Spark FIFO scheduler schedules the tasks of different stages according to the submission order. 
% 	SCache sets the priorities of tasks according to the submission time of each shuffle.
% 	% For a FAIR scheduler, Spark balances the resource among task sets, which leads to a higher priority for those having more tasks unfinished. 
% 	% So SCache sets priorities from high to low in a descending order of remaining storage units of a shuffle. 
% 	% For a FIFO scheduler, Spark schedules the task set that is submitted first. 
% 	% So SCache sets the priorities according to the submit time of each shuffle unit.
% 	\item Intra-shuffle: The intra-shuffle priorities are determined according to the task scheduling inside a stage.
% 	For example Spark schedules tasks with smaller ID at first. 
% 	Based on this, SCache can assign the lower priority to storage units with a larger task ID.
% \end{itemize}
